An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2020-05-23 gas-adsorption/gas-ads-appendix.tex
made a number of changes but couldnt get line numbering working with figures and math.

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{four-cases-pro}
    \caption{Two pairs of boxes containing gas with one of the pair being
    filled with MOF. One box of each sort has a density of gas $\rhofull$
    corresponding to $\pfull$ in the MOF system, while the other two boxes has
    gas density $\rhoempty$}
    \label{fig:delta-gst-maximum}
\end{figure}

\section{An upper bound when $\gst(\rho)$ is monotonic}\label{sec:monotonic}
Every MOF has a $\Delta g_\text{st}$ at a full and empty pressure corresponding
to a full and empty density. The deliverable capacity of the MOF is equal to
the difference between the full and empty density. Examining
Fig.~\ref{fig:methane-gst}, we see that a significant variety of known
experimental $\Delta g_\text{st}$ curves are monotonic. Furthermore, our
qualitative argument in Section~\ref{sec:upper-bound} suggests that this
function \emph{should} monotonically increase for rigid substrates, as
increasing the density of gas causes some of the gas to reside in higher-energy
sites. If this is always the case, the deliverable capacity will always be
bounded by our theoretical upper bound, even for a value of $\V$ that is not
optimal.

@@

Taken together, this indicates that not only is our absolute upper bound an
upper bound for rigid MOFs, but the green curve labeled $\rho_D(\gst)$ in
Figs.~\ref{fig:methane-298-D}, \ref{fig:hydrogen-298-D}, and
\ref{fig:hydrogen-77-D} is an upper bound for materials with a non-optimal
$\gst$.

\section{Cryogenic hydrogen storage}\label{sec:cryo-hydrogen}
\begin{figure}
    \centering
    FIGURE HERE A B C D
    \includegraphics[width=0.95\columnwidth]{hydrogen-77-n-vs-G}
    \caption{Deliverable capacity of hydrogen at liquid nitrogren temperature as a function of the attractive Gibbs free energy $\gst$. Experimental deliverable capacities for several MOFs (data from Ref.~\cite{garcia2018benchmark}) are shown along with the experimental values for $\gst$ at the empty and full pressures shown as $+$'s connected by a line.}
    \label{fig:hydrogen-77-D}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{four-cases-pro}
    \caption{Two pairs of boxes containing gas with one of the pairs
    filled with MOF. One box of each sort has a density of gas $\rhofull$
    corresponding to $\pfull$ in the MOF system, while the other two boxes has
    gas density $\rhoempty$}
    \label{fig:delta-gst-maximum}
\end{figure}

\section{An upper bound when $\gst(\rho)$ is monotonic}\label{sec:monotonic}
Every MOF has a $\Delta g_\text{st}$ at $\pfull$ and $\pempty$ corresponding
to a full and empty density. The deliverable capacity of the MOF is equal to
the difference between the full and empty density. Examining
Fig.~\ref{fig:methane-gst}, we see that a significant variety of known
experimental $\Delta g_\text{st}$ curves are monotonic. Furthermore, our
qualitative argument in Section~\ref{sec:upper-bound} suggests that this
function \emph{should} monotonically increase for rigid substrates, as
increasing the density of gas causes some of the gas to reside in higher-energy
sites. If this is always the case, the deliverable capacity will always be
bounded by our theoretical upper bound, even for a value of $\V$ that is not
optimal.

@@

Taken together, this indicates that not only is our absolute upper bound an
upper bound for rigid MOFs, but the green curve labeled $\rho_D(\gst)$ in
Figs.~\ref{fig:methane-298-D}, \ref{fig:hydrogen-298-D}, and
\ref{fig:hydrogen-77-D} is an upper bound for materials with a non-optimal
$\gst$ at either $\pfull$ or $\pempty$.

\section{Cryogenic hydrogen storage}\label{sec:cryo-hydrogen}
\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{hydrogen-77-n-vs-G}
    \caption{Deliverable capacity of hydrogen at 77\ K as a function of the attractive Gibbs free energy $\gst$. Experimental deliverable capacities for several MOFs (data from Ref.~\cite{garcia2018benchmark}) are shown along with the experimental values for $\gst$ at the empty and full pressures shown as $+$'s connected by a line.}
    \label{fig:hydrogen-77-D}
\end{figure}
